%-------------------------------------------------------------------------------
% yoshimi-cookbook
%-------------------------------------------------------------------------------
%
% \file        yoshimi-cookbook.tex
% \library     Documents
% \author      Chris Ahlstrom
% \date        2015-07-12
% \update      2016-04-21
% \version     $Revision$
% \license     $XPC_GPL_LICENSE$
%
%     This document provides LaTeX documentation for yoshimi.  It is similar
%     in structure to the yoshimi-doc project.
%
%-------------------------------------------------------------------------------

\documentclass[
 11pt,
 twoside,
 a4paper,
 headinclude,
 footinclude,
 final                                 % versus draft
]{article}

% This file and its clone in yoshimi-doc should be kept in sync:

\input{yoshimi-docs-structure}         % specifies document structure and layout

% Replacing normal header/footer with a fancier version.  These two symbols of
% document class were showing up as "unused" in the log file.
%
% headinclude,
% footinclude,
%
% So we add the fancyhdr package, clear the default layout, and set it up for
% our wider pages.

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyheadoffset{0.005\textwidth}
\lhead{Yoshimi Software Synthesizer}
\chead{}
\rhead{Cookbook}
\lfoot{}
\cfoot{\thepage}
\rfoot{}

\makeindex

\begin{document}

\title{A Yoshimi Cookbook}
\author{Chris Ahlstrom\\
   (\texttt{ahlstromcj@gmail.com})}
\date{\today}
\maketitle
\tableofcontents
\listoffigures                         % print the list of figures
\listoftables                          % print the list of tables

% Change the paragraph style to remove indenting and put a line between each
% paragraph.  This could be moved up into the preamble, but then would
% affect the spacing of the TOC and LOF, LOT noted above.

\setlength{\parindent}{0pt}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}

\section{Introduction}
\label{sec:introduction}

   This document is a follow-on to the author's
   "A Yoshimi User Manual" \cite{yoshimidoc}.
   The user manual attempts complete coverage of the user-interface and
   concepts behind \textsl{Yoshimi}.
   This cookbook attempts to provide recipes to solve some common problems
   in getting \textsl{Yoshimi} to perform at its best for the user.

\subsection{Project Structure}
\label{subsec:introduction_project_structure}

   The "Yoshimi Cookbook" project consists of two parts:

   \begin{itemize}
      \item The source material for this document.
      \item A self contained "yoshimi" configuration and data
            section to support the examples in this cookbook.
   \end{itemize}

   The documentation source-files are provided in the \texttt{tex}
   directory.  They are use to create the cookbook via Makefiles and
   the external "latexmk" project.  The result of a "make" is a new
   PDF of the cookbook in the \texttt{pdf} directory.  The latest
   PDF is always provided there so that one does not have to install the
   external projects needed to create it.

   The configuration, banks, presets, and instrument files can be used
   to supplement or replaces the user's own configuration and data files.

\subsection{XML File Compression}
\label{subsec:introduction_xml_files}

   One thing we recommend for following this cookbook is to set the
   \textsl{Yoshimi} compression level to \textbf{0}.  This makes it a lot
   easier to text-edit the file to read its contents and understand them.
   To make this setting:

   \index{XML compression}
   \begin{enumber}
      \item Navigate to \textbf{Menu / Yoshimi / Settings.../ Main settings}.
      \item Click on the left arrow of \textbf{XML compression level} until
         the value of 0 appears.
      \item Click on the \textbf{Save and Close} button.
      \item Restart \textsl{Yoshimi}, then navigate again to this dialog
         to verify that the setting has been saved.
   \end{enumber}

   Setting this option makes the XML files a bit larger, perhaps larger by a
   factor of more than 10, making a 10K file into a 180K file.
   But these days, that should not be a problem.  Maybe if one is running
   \textsl{Yoshimi} on an old \textsl{Raspberry Pi} device.
   On the other hand, for normal usage, it is best to leave the compression
   setting at 3, since decompression is faster than reading larger amounts of
   data from a file.

\subsection{What Game Shall We Play Today?}
\label{subsec:introduction_what_game}

   There are a number of recipes that are hinted at in the user manual, but
   that solve problems that the author has encountered while using
   \textsl{Yoshimi}.

   \begin{itemize}
      \item \textbf{Banks and MIDI}.
         \textsl{Yoshimi} has had recent modifications to support
         bank-switching and using program-change messages to make
         \textsl{Yoshimi} a more flexible MIDI playback tool.
      \item \textbf{General MIDI}.
         It should be possible to set up one or more banks that
         are General MIDI compliant.
      \item \textbf{Usage of Modulators}.
         \textsl{Yoshimi} provides a number of modulation setups,
         but it isn't clear how to use them, especially the ring modulator.
      \item \textbf{Creation of Special Instruments}.
         There are some instruments that don't seem to have
         decent \textsl{ZynAddSubFX}/\textsl{Yoshimi} instrument files.
         Some examples, based on our desires: sitar, koto, bagpipes, steel
         drums, telephone tones, middle-eastern pipes, Japanese instruments,
         that steel-whip percussion sound heard in many songs....
      \item \textbf{More!}.
   \end{itemize}

   This document explains how to do some of the above tasks.

%  Oh, before you get started, go to
%  \textsl{Menu / Instruments / Open Instruments...} and
%  navigate to where you installed this project (for example,
%  \texttt{~/3rdparty/yoshimi-cookbook/yoshimi/banks} and click
%  \textbf{Add to Favorites} in the \textbf{Favorites} dropdown.
%  That's where we store our GM bank and the demonstration files.

\rhead{\rightmark}         % shows section number and section name

% Concepts

\input{cookbook_concepts}

% Presets

\input{cookbook_presets}

% Instruments

\input{cookbook_instruments}

% Banks and General MIDI

\input{cookbook_banks}

% Usage with Various Sequencers

\input{cookbook_sequencers}

% \input{cookbook_concepts}

\section{Summary}
\label{sec:summary}

   In summary, we can say that you will absolutely love 
   cooking with \textsl{Yoshimi}.

% References

\input{cookbook_references}

\printindex

\end{document}

%-------------------------------------------------------------------------------
% vim: ts=3 sw=3 et ft=tex
%-------------------------------------------------------------------------------
